---
title: "Gov 50 Final Project"
author: "Isabella Alas"
description: "Final project"
output:
  distill::distill_article:
    self_contained: false
---

```{r}
library(tidyverse)
library(dplyr)
library(ggplot2)
```

```{r}
Covid19 <- read_csv("COVID-19_Daily_Counts_of_Cases__Hospitalizations__and_Deaths.csv")
```

## Introduction

How many individuals died after being hospitalized by COVID-19 in New York City? COVID-19 affected so many individuals across the globe. Specifically in New York City, the city that never sleeps, the amount of people who were affected by this pandemic was significantly larger than most cities. Between the lockdowns, the limited amount of work, and the increasing death rates, it affected various aspects of daily life for everyone. Because of the densely populated city, the spread of this virus increased rapidly. Many people soon became hospitalized and because of the unknown treatment to this virus, people began dying. There was not enough space to quarantine everyone in the close proximity which led to an increasing amount of deaths. Some people were checked in the hospital one day and died the next. In my project I analyze how the hospitalized count increased rapidly and how the death count quickly increased in a matter of days as the virus spread throughout the city.

## Data

My data set is from COVID-19 Daily Counts of Cases, Hospitalizations, and Deaths from DATA.GOV. This dataset includes many variables: date_of_interest, case_count, probable_case_count, hospitalized_count, death_count. The main variables that I focused on were date_of_interest, hospitalized_count, and death_count. This is a very broad dataset with a starting data of 2/29/2020 and is continuing to be updated till this day. All of the other variables in this dataset are very broad that I didn't think would add to my goal of analyzing the increasing death counts to hospitalized counts.

In these visualizations these plots compare the Hospitalized count of COVID-19 compared to the death count from COVID-19. This shows a positive growth between both the Hospitalized and death counts from COVID-19. This shows that many of the hospitalized and death counts were small and increased very quickly at some points. As the graph moves along it shows that at least half of the hospitalized counts were death counts.

```{r}
ggplot(data = Covid19,
       mapping = aes(x = HOSPITALIZED_COUNT,
                     y = DEATH_COUNT)) +
  geom_point()
```

```{r}
ggplot(data = Covid19, 
       mapping = aes(x = HOSPITALIZED_COUNT,
                     y = DEATH_COUNT)) +
  geom_point() +
  geom_smooth(method = "loess", se = FALSE) +
  scale_x_log10() +
  labs(
    x = "Hospitalized Count",
    y = "Death Count", 
    title = "Hospitalized and Death Count"
  )
```

## Conclusion

In conclusion, there is a clear relationship between the increasing death rates between hospitalized rates as time increases. This shows that many individuals soon died because of the increasing spread of the virus that had no cure at the time. This was just one of the major cities that was greatly affected by the virus. This data can differ for many cities because of the way that either the virus was handled or how the city layout is. Because of the close proximity that New York is, there was no space for individuals to go to escape the virus therefore causing the spread to increase more rapidly compared to flatter more spaced out cities. The fact that there was also no cure for this virus is a significant factor to why this resulted in more death rates. As one of the largest cities in the world, New York had one of the biggest impacts of the virus. It would be ideal to compare other cities together to see how it might differ and if the amount of death rates was lower for those that were hospitalized.
